---
title: "Week3_assignment <br> Salaries by Age <br> and Seniority"
author: "Jerome Cholewa"
date: "March 6th 2017"
output: ioslides_presentation
---

```{r setup, include=FALSE}
knitr::opts_chunk$set( comment = "")
library(plotly)
```

## Salaries by Age and by Seniority
### The Data Set
This data set is a made-up set of salaries by department (no need to explain each department name here), by age and by company seniority
``` {r, message = FALSE, include = FALSE }
SALARY2 <- data.frame(Name.Code = c("SAC1", "SAC2", "CAD2", "CAD5", "CAE2", 
                                    "CAE3", "PAE1", "PAE2", "PAE6", "PAE8", 
                                    "PAE10", "PAE12", "Assistant", "Lab" ),
                      Dept = c("SAC","SAC", "CAD", "CAD", "CAE", "CAE", "PAE",
                               "PAE", "PAE", "PAE", "PAE", "PAE", "Assistant",
                               "LAB"),
                     Salary.2016.MKRW = c(58.4, 63.1, 59.4, 64.2, 60.6, 41.3,
                                          40.0, 43.2, 62.5, 55.7, 49.7, 53.8,
                                          30.4, 71.5),
                     Company.Seniority = c(3.1, 1.1, 22.0, 22.3, 2.9, 2.3, 
                                           4.6, 5.8, 8.9, 2.5, 1.6, 1.3, 3.2,
                                           24.2) ,
                     Age = c(39.9, 39.9, 46.2, 45.8, 39.0, 32.0, 29.4, 32.1,
                             41.5, 39.5, 39.9, 38.1, 32.0, 48.5))
```
`
plot_ly(data = SALARY2, x = ~Company.Seniority, y = ~Age,  
        z = ~Salary.2016.MKRW, type = "scatter3d", color = ~Dept,
        text = ~Name.Code)
`

## THE PLOT
This 3D scatter plot made in plot_ly shows that there is no clear correlation between seniority and salary, but there is a trend of salary going up with age.
```{r plot, message = FALSE, warning = FALSE, , echo = FALSE}
plot_ly(data = SALARY2, x = ~Company.Seniority, y = ~Age, 
        z = ~Salary.2016.MKRW, type = "scatter3d", color = ~Dept,
        text = ~Name.Code)
```
